Response to the defense feedback

### 2021-06-01 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsubsection{Noiseless Lossless Channel}
An information channel is noiseless and lossless if

\begin{equation} \label{chapter5:eq4}
  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
\end{equation}
$|K|$ represents the number of possible variables in $K$.

@@

\subsubsection{Noiseless Loss Channel}
In reality, noiseless loss channel is more common. We define the channel is noiseless loss if

@@

Figure~\ref{fig:channel}(b) shows the example of the type of the channel. Once the input symbol is determined, the output symbol is also determined. Shown in Figure~\ref{fig:channel}(b), the channel has the unique output ($o \in O$) for every input ($k \in K$).

>>>>

\subsubsection{Noiseless Lossless Channel}
An information channel is noiseless and lossless if every $k$ corresponds to exactly one unique $o$. The channel capacity of a noiseless lossless channel equals to
\begin{equation} \label{chapter5:eq4}
  C(K;O) = \max_{p(k)} I(K;O) = \max_{p(k)} H|O| =\max_{p(k)} H|K|
\end{equation}
$|K|$ represents the number of possible variables in $K$.

@@

\subsubsection{Noiseless Loss Channel}
In reality, noiseless loss channel is more common. The channel capacity of a noiseless loss channel equals to

@@

Figure~\ref{fig:channel}(b) shows an example of the type of the channel. Once the input value is determined, the output value is also determined. Shown in Figure~\ref{fig:channel}(b), the channel has the unique output ($o \in O$) for every input ($k \in K$).
